paper1_results_figs_slimmed_50

### 2016-03-16 paper1_results_figs_slimmed_50.Rmd
updating paper figures

## Main Figures for paper 1 : version 4 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed_50.Rmd

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='lightgrey', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  #df_same = ggSubset[which(ggSubset$mixA_minus_seq0.5==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
  #(Intercept)           x 
  #  0.9790948   0.6095132 
  #l_mod$coefficients
  #(Intercept)          x1 
  #1.019330    0.560508

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_diff))+

@@

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )
```

>>>>

## Main Figures for paper 1 : version 5 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed_50.Rmd

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
  #(Intercept)          x1 
  #1.019330    0.560508

@@

  df_20pc <- ggSubset[which(ggSubset$mixA_minus_seq0.5 / ggSubset$gen_cP0.5seq > 0.19 & 
                            ggSubset$mixA_minus_seq0.5 / ggSubset$gen_cP0.5seq < 0.21  ),]

  #remove column it is faceted on to get line in both facets
  col_indices <- colnames(df_20pc) != 'mixA_not20pc_better_seq0.5'
  df_20pc <- df_20pc[,col_indices]

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

@@

             theme_bw() +
             theme(legend.position = "bottom") +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             #geom_smooth(data=df_same, method = "lm", se = FALSE)
             #todo change to where exactly 20% diff
             geom_smooth(data=df_20pc, method = "lm", se = FALSE,colour='red', lwd=0.5)+
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=df_20pc, size=0.8, colour='red', shape=2) #, fill='white') 
           )

  # doing the lm outside of ggplot    
  x1=df_20pc$exposure 
  y1=df_20pc$effectiveness_insecticide1 + df_20pc$effectiveness_insecticide2

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
# (Intercept)          x1 
#   1.3914547   0.2904911
